A generalization of the Bradley-Terry model for draws in chess

### 2025-02-05 inst/collusion_chess_draws.Rnw
consistentification of .bib file

Many situations involve pairwise comparisons that amount to a
Bernoulli trial.  The canonical application would be two-way
competitive situations such as tennis in which one player is
identified as the winner.  The Bradley-Terry model~\citep{bradley1952}
considers~$n$ players and assigns a non-negative number $p_i$ to player
$i$, with $\sum p_i=1$.  Then player $i$ beats player $j$ with
probability $\frac{p_i}{p_i+p_j}$.  This simple system has been
modified and extended many times, for example to account for multi-way
competitions such as {\em MasterChef Australia}~\citep{hankin2017},
and non-competitive situations such as consumer
behaviour~\citep{hankin2010} and mating preference~\citep{west2008}.

@@

The Method of Support \citep{edwards1972} involves only numerical
optimization (not integration which is computationally expensive).
The analysis presented here uses the framework of the
R~\citep{rcore2019} \pkg{hyper2} package~\citep{hankin2017} as a
convenient and unified interface.  Because gradients are available,
convergence to the evaluate is generally rapid and hypothesis-specific
constraints on parameter space are, in general, linear and
straightforward to implement.  The total runtime for all the tests
presented here is less than a few seconds on a desktop PC.

@@

\bibliography{chess}
\end{document}

>>>>

Many situations involve pairwise comparisons that amount to a
Bernoulli trial.  The canonical application would be two-way
competitive situations such as tennis in which one player is
identified as the winner.  The Bradley-Terry model~\citep{bradley1952}
considers~$n$ players and assigns a non-negative number $p_i$ to player
$i$, with $\sum p_i=1$.  Then player $i$ beats player $j$ with
probability $\frac{p_i}{p_i+p_j}$.  This simple system has been
modified and extended many times, for example to account for multi-way
competitions such as {\em MasterChef Australia}~\citep{hankin2017_rnw},
and non-competitive situations such as consumer
behaviour~\citep{hankin2010} and mating preference~\citep{west2008}.

@@

The Method of Support \citep{edwards1972} involves only numerical
optimization (not integration which is computationally expensive).
The analysis presented here uses the framework of the
R~\citep{rcore2019} \pkg{hyper2} package~\citep{hankin2017_rnw} as a
convenient and unified interface.  Because gradients are available,
convergence to the evaluate is generally rapid and hypothesis-specific
constraints on parameter space are, in general, linear and
straightforward to implement.  The total runtime for all the tests
presented here is less than a few seconds on a desktop PC.

@@

\bibliography{hyper2}
\end{document}
